---
title: "Single-Trait Single-Environment Analysis - NE 2006_CAMPO_MOURAO"
output: pdf_document
chunk_output_type: console
---
# Load BLUEs


Load BLUEs from grain yield (GY), grain moisture (GM) and number of ears (NE)

```{r eval=FALSE, message=FALSE}
BLUEs <- read.table("BLUEs.txt", sep = "\t", h = TRUE, stringsAsFactors = F)
```

Select the BLUEs from trait NE and environment 2006_CAMPO_MOURAO

```{r eval=FALSE, message=FALSE}
library("dplyr")

BLUEs_selected <- filter(BLUEs, Env == "2006_CAMPO_MOURAO")
BLUEs_NE <- select(BLUEs_selected, c("H", "Env", "NE_BLUE"))
```


# Load H matrix

```{r eval=FALSE, message=FALSE}
load("Hinv.RData")
```

Select in the H matrix only the hybrids from environment 2006_CAMPO_MOURAO

```{r eval=FALSE, message=FALSE}
idx = as.character(unique(BLUEs_NE$H))
Hmatrix = AHAT.inv[idx,idx]
dim(Hmatrix) 
```


# Adjust the predictive model using MCMCglmm


Set the number of iterations, thin and burnin

```{r eval=FALSE, message=FALSE}
library(MCMCglmm)
nitt=30000
thin=5
burnin= 6000
Hinv = as(Hmatrix,"dgCMatrix") # transform to sparse matrix
```

Declare the prior

```{r eval=FALSE, message=FALSE}
n.env = 1
prior.NonIformative.stse <- list(R = list(V = diag(n.env)/n.env, n =0.002), 
                                 G = list( G1 = list(V = diag(n.env)/n.env, n = 0.002)))

```


Adjust the predictive model using a 5 folds cross-validation scheme 

```{r, eval=FALSE, message=FALSE}
set.seed(156423) 
acc_mcmcglmm <- vector(length=5)
n_folds <- 1:5
sets<-sample(c(rep(n_folds, each=20))) # CV 5 folds

for(fold in n_folds){
  tst<- which(sets ==  fold) # separating the sets from test population
  ytest <- BLUEs_NE[tst, c(1,3) ,drop= FALSE]

  print(paste('Model STSE.NE_2006_CM', fold))

  STSE.NE_2006_CM = MCMCglmm(NE_BLUE ~ 1,
                    random= ~ H,
                    ginverse=list(H=Hinv),
                    data = BLUEs_NE[-tst,], 
                    prior=prior.NonIformative.stse,
                    pr=TRUE,
                    nitt=nitt, thin=thin, burnin=burnin)


  blups = colMeans(STSE.NE_2006_CM$Sol)
  predicted_NE = data.frame(H=gsub("H.H","H",names(blups)),blups)
  predicted_and_observed_NE = merge(BLUEs_NE,predicted_NE,by="H")
  final_NE = predicted_and_observed_NE[tst,]
  acc_mcmcglmm[fold] <- cor(final_NE[,3],final_NE[,4])

}

save.image("2006_CAMPO_MOURAO_NE_CV.RData")
```



