---
title: "Single-Trait Multi-Environment (STME) analysis using the same training/testing partition of Single-Environment (SE) analysis - GM 2008"
output: pdf_document
chunk_output_type: console
---
# Load BLUEs


Load BLUEs from grain yield (GY), grain moisture (GM) and number of ears (NE)

```{r eval=FALSE, message=FALSE}
BLUEs <- read.table("BLUEs.txt", sep = "\t", h = TRUE, stringsAsFactors = F)
```

Select the BLUEs from trait GM 

```{r eval=FALSE, message=FALSE}
library(dplyr)
BLUEs_GM <- select(BLUEs, c("H", "Env", "GM_BLUE"))
```

Create a column env_hybrid

```{r eval=FALSE, message=FALSE}
BLUEs_GM$env_hybrid <- paste("Env",BLUEs_GM$Env , sep = "", BLUEs_GM$H)
```

Select the year 2008 as testing set

```{r eval=FALSE, message=FALSE}
BLUEs_tst <- BLUEs_GM[BLUEs_GM$Env == "2008_CAMPO_MOURAO",]
```



# Load H matrix

```{r eval=FALSE, message=FALSE}
load("Hinv.RData")
dim(AHAT.inv)
```


# Adjust the predictive model using MCMCglmm


Set the number of iterations, thin and burnin

```{r eval=FALSE, message=FALSE}
library(MCMCglmm)
nitt=30000
thin=5
burnin=6000
Hinv = as(AHAT.inv,"dgCMatrix") # transform to sparse matrix
```

Declare the prior

```{r eval=FALSE, message=FALSE}
n.env = 4
prior.NonIformative.me <- list(R = list(V = diag(n.env)/n.env, n =0.002), 
                               G = list( G1 = list(V = diag(n.env)/n.env, n = 0.002)))
```


Adjust the predictive model using a 5 folds cross-validation scheme but using year 2008 as testing set

```{r, eval=FALSE, message=FALSE}
set.seed(156423) 
acc_mcmcglmm <- vector(length=5)
n_folds <- 1:5

sets<-sample(c(rep(n_folds, each=20))) # CV 5 folds
for(fold in n_folds){
  
  tst<- which(sets ==  fold) # separating the sets from test population
  ytest <- BLUEs_tst[tst,4, drop= FALSE]
  names_test <- rownames(ytest)
  posi_test <- match(names_test, rownames(BLUEs_GM))
 
    
  print(paste('Model STME.GM_CV_2008_TST', fold))
  
  STME.GM_CV_2008_TST =  MCMCglmm(GM_BLUE ~ -1 + Env,
                    random= ~us(Env):H,
                    ginverse=list(H=Hinv),
                    rcov = ~ us(Env):units,
                    data = BLUEs_GM[-posi_test,], 
                    prior=prior.NonIformative.me,
                    pr=TRUE,
                    nitt=nitt, thin=thin, burnin=burnin)
  
  
  blups = colMeans(STME.GM_CV_2008_TST$Sol)
  predicted_gm = data.frame(env_hybrid=gsub(".H.H","H",names(blups)),blups)
  predicted_and_observed_gm = merge(BLUEs_GM,predicted_gm,by="env_hybrid")
  final_gm = predicted_and_observed_gm[tst,]
  acc_mcmcglmm[fold] <- cor(final_gm[,4],final_gm[,5])
  }  

save.image("STME_GM_CV_2008_TST.RData")  
```



