---
title: "Multi-Trait Multi-Environment (MTME) analysis using the same training/testing partition of Single-Environment (SE) analysis - 2008"
output: pdf_document
chunk_output_type: console
---
# Load BLUEs


Load BLUEs from grain yield (GY), grain moisture (GM) and number of ears (NE)

```{r eval=FALSE, message=FALSE}
BLUEs <- read.table("BLUEs.txt", sep = "\t", h = TRUE, stringsAsFactors = F)
```

Scale traits 

```{r eval=FALSE, message=FALSE}
library(dplyr)
MT_scale <- scale(select(BLUEs, c("GY_BLUE", "GM_BLUE", "NE_BLUE")))
MT_scale <- cbind(select(BLUEs, c("H", "Env")), MT_scale)
```

Create a column env_trait

```{r eval=FALSE, message=FALSE}
GY_scale <- select(MT_scale, c("H", "Env", "GY_BLUE"))
GY_scale$trait_env <- paste(GY_scale$Env , sep = "_", "GY")
colnames(GY_scale) <- c("H", "env", "BLUES", "trait_env")


NE_scale <- select(MT_scale, c("H", "Env", "NE_BLUE"))
NE_scale$trait_env <- paste(NE_scale$Env , sep = "_", "NE")
colnames(NE_scale) <- c("H", "env", "BLUES", "trait_env")

GM_scale <- select(MT_scale, c("H", "Env", "GM_BLUE"))
GM_scale$trait_env <- paste(GM_scale$Env , sep = "_", "GM")
colnames(GM_scale) <- c("H", "env", "BLUES", "trait_env")

MT_final <- rbind(GY_scale, NE_scale, GM_scale)
MT_final <- transform(MT_final, trait_env = factor(trait_env))
str(MT_final)
```

Create a column env_trait_hybrid

```{r eval=FALSE, message=FALSE}
MT_final$env_trait_hybrid <- paste(MT_final$trait_env, sep = "", MT_final$H)
```

Select the year 2008 as testing set

```{r eval=FALSE, message=FALSE}
MT_tst <- MT_final[MT_final$env == "2008_CAMPO_MOURAO",]
```


# Load H matrix

```{r eval=FALSE, message=FALSE}
load("Hinv.RData")
dim(AHAT.inv)
```


# Adjust the predictive model using MCMCglmm


Set the number of iterations, thin and burnin

```{r eval=FALSE, message=FALSE}
library(MCMCglmm)
nitt=30000
thin=5
burnin=6000
Hinv = as(AHAT.inv,"dgCMatrix") # transform to sparse matrix
```

Declare the priori

```{r eval=FALSE, message=FALSE}
n.env = 12
prior.NonIformative.me <- list(R = list(V = diag(n.env)/n.env, n =0.002), 
                               G = list( G1 = list(V = diag(n.env)/n.env, n = 0.002)))
```


Adjust the predictive model using a 5 folds cross-validation scheme but using year 2008 as testing set

```{r, eval=FALSE, message=FALSE}
set.seed(156423) 
acc_mcmcglmm_GY <- vector(length=5)
acc_mcmcglmm_NE <- vector(length=5)
acc_mcmcglmm_GM <- vector(length=5)

length_GY <- 100
length_GY_NE <- 200

n_folds <- 1:5
sets<-sample(c(rep(n_folds, each=20))) # CV 5 folds
for(fold in n_folds){
  
  tst_GY <- which(sets ==  fold) # separating the sets from test population
  tst_NE <- tst_GY + length_GY
  tst_GM <- tst_GY + length_GY_NE
  tst_final <- c(tst_GY, tst_NE, tst_GM)
  yteste <- MT_tst[tst_final,, drop=FALSE]
  posi_teste <- match(yteste$env_trait_hybrid, MT_final$env_trait_hybrid)
  

    MTME_CV_2008_TST =MCMCglmm(BLUES ~ -1 + trait_env,
                               random= ~us(trait_env):H,
                               ginverse=list(H=Hinv),
                               rcov = ~ us(trait_env):units,
                               data = MT_final[-posi_teste,], 
                               prior=prior.NonIformative.me,
                               pr=TRUE,
                               nitt=nitt, thin=thin, burnin=burnin)

    a_gy = colMeans(MTME_CV_2008_TST$Sol)
    idx_gy = grep("CAMPO_MOURAO_GY.H.",names(a_gy))
    predicted_gy = data.frame(H=gsub("trait_env","",names(a_gy[idx_gy])),a_gy[idx_gy])
    predicted_gy$env_trait_hybrid = gsub(".H.H", "H", predicted_gy$H)
    predicted_and_observed_gy =    
    merge(MT_final[,c(3,5)],predicted_gy,by="env_trait_hybrid")
    final_gy = predicted_and_observed_gy[tst_GY,]
    acc_mcmcglmm_GY[fold] <- cor(final_gy[,2],final_gy[,4])

    a_ne = colMeans(MTME_CV_2008_TST$Sol)
    idx_ne = grep("CAMPO_MOURAO_NE.H.",names(a_ne))
    predicted_ne = data.frame(H=gsub("trait_env","",names(a_ne[idx_ne])),a_ne[idx_ne])
    predicted_ne$env_trait_hybrid = gsub(".H.H", "H", predicted_ne$H)
    predicted_and_observed_ne = 
    merge(MT_final[,c(3,5)],predicted_ne,by="env_trait_hybrid")
    final_ne = predicted_and_observed_ne[tst_GY,]
    acc_mcmcglmm_NE[fold] <- cor(final_ne[,2],final_ne[,4])

    a_gm = colMeans(MTME_CV_2008_TST$Sol)
    idx_gm = grep("CAMPO_MOURAO_GM.H.",names(a_gm))
    predicted_gm = data.frame(H=gsub("trait_env","",names(a_gm[idx_gm])),a_gm[idx_gm])
    predicted_gm$env_trait_hybrid = gsub(".H.H", "H", predicted_gm$H)
    predicted_and_observed_gm = 
    merge(MT_final[,c(3,5)],predicted_gm,by="env_trait_hybrid")
    final_gm = predicted_and_observed_gm[tst_GY,]
    acc_mcmcglmm_GM[fold] <- cor(final_gm[,2],final_gm[,4])

}

save.image("MTME_CV_2008_TST.RData")  
```



