---
title: "Multi-Trait Single-Environment Analysis"
output: pdf_document
chunk_output_type: console
---
# Load BLUEs


Load BLUEs from grain yield (GY), grain moisture (GM) and number of ears (NE)

```{r eval=FALSE, message=FALSE}
BLUEs <- read.table("BLUEs.txt", sep = "\t", h = TRUE, stringsAsFactors = F)
```

Select the BLUEs from environment 2009_CAMPO_MOURAO

```{r eval=FALSE, message=FALSE}
library("dplyr")

BLUEs_selected <- filter(BLUEs, Env == "2009_CAMPO_MOURAO")
```

Scale traits 

```{r eval=FALSE, message=FALSE}
MT_scale <- scale(select(BLUEs_selected, c("GY_BLUE", "GM_BLUE", "NE_BLUE")))
MT_scale <- cbind(select(BLUEs_selected, c("H", "Env")), MT_scale)
```

# Load H matrix

```{r eval=FALSE, message=FALSE}
load("Hinv.RData")
```

Select in the H matrix only the hybrids from environment 2009_CAMPO_MOURAO

```{r eval=FALSE, message=FALSE}
idx = as.character(unique(MT_scale$H))
Hmatrix = AHAT.inv[idx,idx]
dim(Hmatrix) # 125 x 125
```


# Adjust the predictive model using MCMCglmm

Set the number of iterations, thin and burnin

```{r eval=FALSE, message=FALSE}
library(MCMCglmm)
nitt=30000
thin=5
burnin=6000
Hinv = as(Hmatrix,"dgCMatrix") # transform to sparse matrix
```

Declare the prior

```{r eval=FALSE, message=FALSE}
n.trait = 3
prior.NonIformative.mt <- list(R = list(V = diag(n.trait)/n.trait, n =0.002), 
                               G = list( G1 = list(V = diag(n.trait)/n.trait, 
                                   n = 0.002)))

```


Adjust the predictive model using a 5 folds cross-validation scheme 

```{r eval=FALSE, message=FALSE}
set.seed(156423) 
blups <- list()
ind_test <- list()

acc_mcmcglmm_GY <- vector(length=5)
acc_mcmcglmm_NE <- vector(length=5)
acc_mcmcglmm_GM <- vector(length=5)


n_folds <- 1:5
sets<-sample(c(rep(n_folds, each=25))) # CV 5 folds

for(fold in n_folds){
  
  tst<- which(sets ==  fold) # separating the sets from test population
  ytest <- MT_scale[tst, ,drop= FALSE]
  MT_trn <- MT_scale[-tst,]
  

  print(paste('Model MTSE.2009_CM', fold))

  MTSE.2009_CM = MCMCglmm(cbind(GY_BLUE, GM_BLUE, NE_BLUE) ~ trait -1 ,
                 random= ~ us(trait):H,
                 ginverse=list(H=Hinv),
                 rcov = ~ us(trait):units,
                 data = MT_trn, 
                 prior=prior.NonIformative.mt,
                 family = rep("gaussian", 3),
                 pr=TRUE,
                 nitt=nitt, thin=thin, burnin=burnin)

blups[[fold]] = colMeans(MTSE.2009_CM$Sol)
ind_test[[fold]] = ytest$H

# Extracting the accuracy from GY
a_gy = colMeans(MTSE.2009_CM$Sol)
idx_gy = grep("traitGY_BLUE.H.",names(a_gy)) 
predicted_gy = data.frame(H=gsub("traitGY_BLUE.H.","",names(a_gy[idx_gy])),a_gy[idx_gy])
predicted_and_observed_gy = merge(MT_scale[,c(1,3)],predicted_gy,by="H")
final_gy = predicted_and_observed_gy[tst,]
acc_mcmcglmm_GY[fold] <- cor(final_gy[,2],final_gy[,3])

# Extracting the accuracy from NE
a_ne = colMeans(MTSE.2009_CM$Sol)
idx_ne = grep("traitNE_BLUE.H.",names(a_ne)) 
predicted_ne = data.frame(H=gsub("traitNE_BLUE.H.","",names(a_ne[idx_ne])),a_ne[idx_ne])
predicted_and_observed_ne = merge(MT_scale[,c(1,5)],predicted_ne,by="H")
final_ne = predicted_and_observed_ne[tst,]
acc_mcmcglmm_NE[fold] <- cor(final_ne[,2],final_ne[,3])

# Extracting the accuracy from GM
a_gm = colMeans(MTSE.2009_CM$Sol)
idx_gm = grep("traitGM_BLUE.H.",names(a_gm)) 
predicted_gm = data.frame(H=gsub("traitGM_BLUE.H.","",names(a_gm[idx_gm])),a_gm[idx_gm])
predicted_and_observed_gm = merge(MT_scale[,c(1,4)],predicted_gm,by="H")
final_gm = predicted_and_observed_gm[tst,]
acc_mcmcglmm_GM[fold] <- cor(final_gm[,2],final_gm[,3])

}

save.image("2009_CAMPO_MOURAO_MT_CV.RData")
```

